\myTitle

### 2014-10-29 tex/main-body-text.tex
changed a figure after looking at distance between qi values from programs
corrected minor typo for Fst value

\section*{Comparison of {\sc structure} and {\sc flock} results}
Data sets with known $K$ were simulated
(code provided on GitHub repository https://github.com/eriqande/flock-comment)
and evaluated in the programs {\sc flock} and {\sc structure} 
for the known value.The first dataset simulated was composed of five populations of 
sizes 500, 500, 800, 1100, and 1100 comprised of individuals 
with 15 loci and an average pairwise $F_{ST} = 0.03$ between populations. 
The second and third dataset were simulated with population sizes
250, 250, 400, 550, and 550 and average pairwise $F_{ST} = 0.02 and 0.03$
respectively. {\sc flock} was run nine times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for the known value of $K$. The no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run nine times with 
a 5,000 sweep burn-in followed by a 20,000 sweep sample from the posterior. 
% Looking back some of the runs were under different conditions, not huge differences. 
% But 1000 burn-in and 5,000 sweep look about the same
All runs were performed on a JNCS D685 with an i7 3.40GHz processor and 8GB
of RAM running 64-bit Windows 7.

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/Simulations_Fig1.pdf}   % Use this if we want it color (I'll make greyscale later)  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
of {\sc flock} made with the program {\sc distruct}. Each horizontal plot represents one of nine individual runs of the program {\sc structure}, or the `best run' from a series of nine runs in {\sc flock} at $K=5$. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
%gray-scale
vertical bar. Simulation 1 was composed of populations of 
size 500, 500, 800, 1100, and 1100 with an average pairwise $F_{ST} = 0.03$ between populations. 
The second and third dataset were simulated with population sizes
250, 250, 400, 550, and 550 and average pairwise $F_{ST} =$ 0.02 and 0.03
respectively.}
    \label{fig:Sims}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
    \includegraphics[width=0.5\textwidth]{images/Figures-Pat/EucliDist.pdf}   % Use this if we want it color (I'll make greyscale later)  
    \caption{Eucledian distance between true $q_i$ value and inferred value from {\sc structure} and {\sc flock} .}
    \label{fig:ED}
\end{center}
\end{figure*}

>>>>

\section*{Comparison of {\sc structure} and {\sc flock} results}
Data sets with known $K$ were simulated
(code provided on GitHub repository https://github.com/eriqande/flock-comment)
and evaluated in the programs {\sc flock} and {\sc structure} 
for the known value.The first dataset simulated was composed of five populations of 
sizes 500, 500, 800, 1100, and 1100 comprised of individuals 
with 15 loci and an average pairwise $F_{ST} = 0.03$ between populations. 
The second and third dataset were simulated with population sizes
250, 250, 400, 550, and 550 and average pairwise $F_{ST} = 0.02 and 0.01$
respectively. {\sc flock} was run nine times using the default setting for all 
run parameters (initial partition = random, number of iterations = 20, number of runs = 50, 
LLOD threshold = 0) for the known value of $K$. The no-admixture, 
uncorrelated-allele-frequency model implemented in {\sc structure} was run nine times with 
a 5,000 sweep burn-in followed by a 20,000 sweep sample from the posterior. 
% Looking back some of the runs were under different conditions, not huge differences. 
% But 1000 burn-in and 5,000 sweep look about the same
All runs were performed on a JNCS D685 with an i7 3.40GHz processor and 8GB
of RAM running 64-bit Windows 7.

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/Simulations_Fig1.pdf}   % Use this if we want it color (I'll make greyscale later)  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
of {\sc flock} made with the program {\sc distruct}. Each horizontal plot represents one of nine individual runs of the program {\sc structure}, or the `best run' from a series of nine runs in {\sc flock} at $K=5$. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
%gray-scale
vertical bar. Simulation 1 was composed of populations of 
size 500, 500, 800, 1100, and 1100 with an average pairwise $F_{ST} = 0.03$ between populations. 
The second and third dataset were simulated with population sizes
250, 250, 400, 550, and 550 and average pairwise $F_{ST} =$ 0.02 and 0.01
respectively.}
    \label{fig:Sims}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
    \includegraphics[width=0.5\textwidth]{images/Figures-Pat/ED_fig2.pdf}   
% HIDEOUS GRAPH, we will talk and I might make one with actual distributions! 
    \caption{Eucledian distance between true $q_i$ value and inferred value from {\sc structure} and {\sc flock} .}
    \label{fig:ED}
\end{center}
\end{figure*}
